% E. Dunham -- Resume
% Contents Copyright (C) 2014 - 2016, E. Dunham

% LaTeX code for rendering the resume is distributed under the MIT license.
% See LICENSE.txt. It means you can use the code for whatever you want,
% including your own resume, but I'm not liable if it catches your computer on
% fire.

% Template originally developed by E. Dunham
% https://github.com/edunham/resume/blob/master/resume.tex

\documentclass[11pt]{article} % Set default font size to 11pt


% Some settings that the stuff hidden in the preamble will reference
\def \whitespaciness { 0 } % pt. bigger numbers = emptier page. 0 is ok.
\def \typeoffill {\dotfill} % hfill makes blank, dotfill makes dotted lines.


\input{preamble}
\begin{document}

\centerline{{\Huge \bf Paul McLanahan}}

\bigskip

\contact{\href{mailto:pmac@pmac.io}{pmac@pmac.io}}
        {\href{https://pmac.io}{pmac.io}}
        {\href{https://github.com/pmac}{github.com/pmac}}
        {Atlanta, Georgia \& Remote}

\heading{Skills}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\center
\emph{Software Engineer with 12 years of experience building and deploying Python web applications}
\linebreak
\emph{and 20 years total in web technology}
\endcenter

\skill{Systems Administration}
      {Linux, K8s, Docker, AWS, GCP, TravisCI, CircleCI, GitLabCI}

\skill{Development}
      {Python, Django, SQL, Bash, HTML/CSS/Javascript}

\skill{Collaboration}
      {IRC/Slack, Git \& GitHub, Sphinx, Bugzilla}

\heading{Employment}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{Mozilla}
           {Staff Backend Software Engineer}
           {08/2019 - present}

\item Developed new CI pipelines using GitLabCI and task runners in our own AWS infrastructure.
These runners build our Docker images, update k8s deployments, and run unit and integration tests.

\item Implemented a new l10n system for \href{https://github.com/mozilla/bedrock/}{www.mozilla.org} (www.m.o)
for over 100 languages, moving the site from custom .lang file format to \href{https://www.projectfluent.org/}{Fluent} files to support
the l10n systems and teams in use around Mozilla.

\item Continued my role as technical lead for www.m.o and basket.m.o, overseeing their performance and reliability.

\item Developed a redirector service for \href{https://github.com/mozmeao/www.firefox.com/}{www.firefox.com} so that Marketing could quickly deploy redirects or host
test pages on this valuable domain.

\experience{Mozilla}
           {Senior Web Developer}
           {10/2013 - 08/2019}

\item Worked as technical lead for the www.m.o and \href{https://github.com/mozmeao/basket/}{basket.m.o} projects for backend development.

\item Moved www.m.o to a hybrid-static site still using Django but
\href{https://mozilla.github.io/meao/2018/03/28/bedrock-the-sqlitening/}{relying on pre-built read-only SQLite files} for
data distribution.

\item Helped move our infra from Deis to pure kubernetes (k8s) by doing a lot of work on the apps and deployment scripts,
as well as \href{https://mozilla.github.io/meao/2018/02/27/django-k8s-elb-health-checks/}{developing and releasing django-allow-cidr}.

\item Moved www.m.o assets pipeline from django-pipeline to Gulp using separate Docker images for each and browser-sync to serve the assets
and proxy the Django app.

\item Lead the technical work for \href{https://blog.mozilla.org/webdev/2014/04/28/celebrating-the-web-we-want/}{webwewant.m.o},
an application that geolocated IPs and showed downloads of Firefox 29 on a map.

\item Built the publishing system for Mozilla Foundation Security Advisories for use by the security team that takes
\href{https://github.com/mozilla/foundation-security-advisories}{Markdown or YAML files in a repo} and turns them into
\href{https://www.mozilla.org/en-US/security/advisories/}{the /security/ section of www.m.o}.

\item Developed an \href{https://github.com/mozilla/nucleus/}{administration platform} and
\href{https://github.com/mozilla/release-notes/}{data exchange} system for
\href{https://www.mozilla.org/en-US/firefox/releases/}{Firefox release notes} management.

\item Developed the standard for \href{https://www.contributejson.org/}{contribute.json} files in repos and on websites.

\experience{Mozilla}
           {Web Developer}
           {01/2012 - 10/2013}

\item Worked with various teams to improve and maintain web applications including mozillians.org, mozillalabs.com, and developer.m.o.

\item Worked on the transition of www.m.o from PHP to a Python/Django application.

\item Worked on basket.m.o to add support for the SMS api from ExactTarget.

\item Developed and deployed \href{https://github.com/mozilla/scrumbugz}{scrumbu.gs}, a site that
\href{https://blog.mozilla.org/webdev/2012/03/27/scrum-and-bugzilla/}{gathered Scrum data from bugs in bugzilla.m.o and graphed it} for teams in
need of that sort of thing.

\experience{MetaMetrics Inc.}
           {Software Engineer}
           {01/2010 - 12/2011}

\item Developed web applications around the company's core educational measurement technologies.

\item Worked on a team to develop and launch engagingenglish.com, a site that aggregates content from across the internet,
measures it for text complexity, and recommends it to users based on their reading skill level and interests.

\item Developed internal web-based tools to increase efficiency and decrease errors for other teams.

\item All development work was done with Python and Django, using many 3rd party libraries including South and Haystack
(in front of Solr), and using MySQL or PostgreSQL for persistence depending on the project.

\experience{Intuit}
           {Software Engineer}
           {2007 - 2009}

\item Worked on the team that designed and built a master configuration management system for all Digital Insight products.
The system manages configuration files, databases, and product files across multiple network tiers and server architectures.
All of the web-based interfaces were built with Python/Django using jQuery for client side JS.

\item Wrote and maintained a variety of CLI and web-based tools to help our web and technical support teams do their jobs more efficiently.
These were built using a variety of technologies including Python, Django, Perl, PHP, and MySQL, and deployed to Debian GNU/Linux and AIX.

\experience{Digital Insight}
           {Senior Web Developer}
           {2005 - 2007}

\item Worked on a team that both built, and managed the building of websites on a variety of platforms from flat files on a Unix server,
to XML/XSLT based sites running on Apache Cocoon. I pioneered the effort to use jQuery as our standard JS library,
and wrote several jQuery plugins to aid our development process. As Sr. Developer, I was also responsible for
maintaining the quality and quantity of the work of the entire team. I also installed, configured, and maintained
the two Ubuntu development servers the team used to host our sites in devlopment as well as the tools we developed
to aid in site development.

\experience{SmallBizPros Inc.}
           {IT Specialist}
           {2004 - 2005}

\item Developed accounting and server management software using Perl, PHP, and PowerBuilder.

\item Installed and managed the Linux server infrastructure for the company providing web and email services.

\experience{Digital Insight}
           {Web Author}
           {2002 - 2004}

\item Built marketing websites for banks and credit unions using just HTML, Javascript, and CSS.

\item Built tools to improve the team's output velocity and quality.

\end{description}

\heading{FLOSS Projects}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\project{\href{https://github.com/pmclanahan/django-celery-email}{django-celery-email}}
        {}
        {Send emails async from Django using Celery}

\project{\href{https://github.com/pmac/django-redirect-urls}{django-redirect-urls}}
        {}
        {Redirects for Django sites in code, not DB}

\project{\href{https://github.com/pmac/urlwait}{urlwait}}
        {}
        {Waits for a service defined in a URL in the environment to become available}

\project{\href{https://github.com/pmac/dokku-webhook-deploy}{dokku-webhook-deploy}}
        {}
        {Use Dokku to auto-deploy branches pushed to Github}

\heading{Education}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{University of Georgia}
           {Master of Internet Technology}
           {2001 - 2002}

Intense masters program setup as a collaboration between the MIS  and CS departments.

\experience{University of Georgia}
           {Bachelor of Science - Cellular Biology}
           {1995 - 1999}

Undergraduate work in genetics and developmental biology.

\end{description}

%\heading{Recent Speaking Engagements}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\squish
%
%\event{Linux.conf.au}
%      {01/2018}
%      {}
%      {Should you rewrite in Rust?}
%
%\event{GitHub Universe}
%      {10/2017}
%      {}
%      {Building a better browser engine on GitHub}
%
%\event{RustFest Kyiv}
%      {04/2017}
%      {Keynote lecture}
%      {Spreading Rust}
%
%\hfill \small ...and more at https://edunham.net/pages/talks.html

\end{document}
